Modular Curves

### 2020-01-27 paper.tex
modular forms on modular curves

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
%\usepackage[dutch]{babel}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{geometry}
\usepackage{tikz-cd}
\usepackage{mdframed}
\usepackage{color}
\usepackage{microtype}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{todonotes}
\usepackage[backend=biber]{biblatex}
\addbibresource{references.bib}
% figure support
\usepackage{import}
\usepackage{xifthen}
\usepackage{pdfpages}
\usepackage{transparent}
\newcommand{\incfig}[1]{%
	\def\svgwidth{\columnwidth}
	\import{./figures/}{#1.pdf_tex}
}

@@

\maketitle

\bigskip

@@

This is the report of the journey of a student learning about elliptic curves. 
This report should be thought of as my notes while working my way through the first chapters of \emph{A First Course in Modular Forms} by Fred Diamond and Jerry Shurman\cite{diamondFirstCourseModular2005a}. 
This book is my main reference. 
Most of this report is paraphrasing this book, but I've added some details where I thought the book was lacking. 
I've also tried to add some visual intuitions I developed to aid my understanding of this material. I hope potential readers will find these useful as well.

@@

\begin{definition}
	The \emph{Modular group} are the $2\times 2$ matrices with integer coefficients and determinant $1$.
	 \[
		 \SL_2(\Z) =   \bigset{\begin{pmatrix} a& b\\ c& d \end{pmatrix}}{a, b, c, d \in \Z, ac - bd = 1}
	.\] 
\end{definition}
It can be shown that the modular group is generated by \[
	\begin{pmatrix}  1 & 1 \\ 0 & 1 \end{pmatrix} 
	\text{ and }
	\begin{pmatrix} 0 & -1 \\ 1 & 0 \end{pmatrix} 
.\] 
For a proof of this we refer to the appendices. 
We now define how this group acts on the complex half plane. 
\begin{definition}
	Let  $\gamma = \begin{pmatrix} a & b \\ c & d \end{pmatrix} $ be any element of $\SL_2\Z$ and $\tau$ be any element of $\mathcal{H} \cup \{\infty\} $.
	The multiplication of these two elements is defined as 
	\[
		\gamma(\tau) = \gamma \cdot \tau = \frac{a \tau + b}{ c \tau + d}
	.\] 
\end{definition}
Note that this group action is well defined. First we have to check that this every $\tau \in \mathcal{H} \cup \{\infty\}  $ gets mapped to another element of $\tau \in \mathcal{H} \cup \{ \infty\}$. 
Note that is is sufficient to check this for the action of the generators, which induce the maps \[
\tau \mapsto  \tau+1 \text{ and } \tau \mapsto \frac{-1}{\tau}
\]
from which it is obvious.
We can also easily see that $I_2 \cdot \tau = \tau$. 
We also see that for $\gamma = \begin{pmatrix} a & b \\ c & d \end{pmatrix} $ and $\beta = \begin{pmatrix} f & g \\ h & i \end{pmatrix} $ is holds that 
\begin{align*}
	\gamma \left( \beta \cdot  \tau\right) &=  \gamma\cdot \frac{f\tau + g}{h \tau + i} \\
					       &= \frac{a\left( \frac{f \tau + g}{h\tau + i} \right) + b}{c \left( \frac{f \tau + g}{h \tau + i} \right) + d} \\	
					       &= \frac{(af + bh)\tau + ga + bi}{(cf + dh) \tau + cg + di} \\
					       &= \begin{pmatrix} af + bh & ag + bi \\ cf + dh & cg + di \end{pmatrix} \cdot \tau \\
					       &= (\gamma \beta)\cdot \tau \\
.\end{align*}

\subsection{Subgroups of the Modular Group} \label{sec:subgroups_of_the_modular_group}
Quite often it will be useful to restrict our focus to subgroups of the modular group. 
The type of subgroup we'll most interested in are the so-called \emph{congruence subgroups}.
To define these we first have to define the so called \emph{principal congruence subgroups}.  
\begin{definition}
	For any $N \in \N$ we define the \emph{principal congruence subgroup of level $N$} to be \[
		\Gamma(N) = \bigset{\begin{pmatrix} a & b \\ c & d \end{pmatrix} \in \SL_2(\Z)}{\begin{pmatrix} a & b \\ c & d \end{pmatrix}  \equiv \begin{pmatrix} 1 & 0 \\ 0 & 1 \end{pmatrix}  (\mathrm{mod}\; N)}
	.\] 
\end{definition}

@@

Some functions on $\mathcal{H} $ are very well behaved under this action.

@@

It's clearly enough so check \eqref{eq:weakly_modular} only for the generators of $\SL_2\Z$. I.e.\begin{equation}\label{eq:sufficient_weakly_modular}
	f(\tau + 1) = f(\tau) \text{ and } f\left(-\frac{1}{\tau}\right)  = \tau^{k}f(\tau)
.\end{equation} 
From this we see that weakly modular functions are $\Z$ periodic.

We will now introduce the weight-$k$ operator on functions $[\gamma]_k$.
 \begin{definition}
	 Let $f: \mathcal{H}  \to \C$ be a function,  $\gamma = \begin{pmatrix} a & b \\ c & d \end{pmatrix} \in \SL_2\Z$ and $k \in \Z$ then we define the function $f[\gamma]_k$ to be 
	  \begin{align*}
		  f[\gamma]_k: \mathcal{H}  &\longrightarrow \C \\
		  \tau &\longmapsto (c\tau + d)^{-k}f(\gamma(\tau))
	 .\end{align*}
\end{definition}
This allows us to characterize  \emph{weakly modular of weight  $k$} as follows.
 \begin{lemma}
	 A function $f: \mathcal{H}  \to \C$ is weakly modular of weight $k$ if and only if for every $\gamma \in \SL_2$: \[
		 f[\gamma]_k = f
	 .\] 
\end{lemma}
In light of this characterization we extend to definition of weakly modular to congruence subsets of $\SL_2\Z$.

\begin{definition}
	Let $\Gamma$ be a congruence subset of $\SL_2\Z$. We say that a function $f: \mathcal{H}  \to \C$ is \emph{weakly modular of weight $k$ with respect to $\Gamma$} if for every  $ \gamma \in \Gamma$:
	 \[
		 f[\gamma]_k = ff[\gamma]_k 
	.\] 
\end{definition}

We are now ready to give the definition of a modular form. 
\begin{definition}\label{def:modular_form}
	Let $\Gamma$ be congruence subgroup of $\SL_2\Z$
	A function $f: \mathcal{H}  \to \C$ is a \emph{modular form of weight $ k$ with respect to $\Gamma$} if 
	\begin{enumerate}
		\item $f$ is holomorphic on $\mathcal{H} $,
		\item $f$ is weakly modular of weight $k$ with respect to $\Gamma$, 
		\item $f[\gamma]_k$ is holomorphic at $\infty$ for every $\gamma \in \SL_2\Z$. 
	\end{enumerate}
	We denote the set of modular froms of weight $k$ with respect to $\Gamma$ as $\mathcal{M} _k(\SL_2\Z)$.

	If $\Gamma = \SL_2\Z$ we say simply that $f$ is a modular form of weight $k$. 
\end{definition}
The stament 'holomorhic at $\infty$' deserves some explanation. There are many equivalent ways of defining it, but for our purposes we will take this to mean that $f$ allows a fourier expansion (not too suprising as  $f$ is $\Z$ periodic)\footnote{The real picture behing holomopich at $\infty$ is that, due to $f$ being $\Z$-periodic, $H$ can be 'rolled up' on the unit disk, where $\infty$ gets mapped to the center. In this picture  $f$ being holomorphic at $\infty$ means that  $f$ allows an extension which holomorphic on the center of the disk.}, i.e.\ \[
	f(\tau) = \sum_{n=0}^{\infty} a_n e^{n 2\pi i \tau}
,\]
for some $a_n \in \C$.
Another equivalent statement is that the limit $\lim_{\im(\tau) \to \infty} f(\tau)$ exists and is finite.

Note that it is only seccesary to verify the 3rd point for a representitive of every coset $\alpha \Gamma$ as by the weak modularity  $f[\alpha]_k = f[\alpha \gamma]_k$ for every  $\gamma \in \Gamma$. 
If  $f$ is a modular form (so $\Gamma = \SL_2\Z$) then we just have to verify that $f$ is holomorphic at $\infty$.
Note that $\mathcal{M}(\Gamma)$ is a $\C$-vector space. 
It turns out that the last condition of \cref{def:modular_form} makes $\mathcal{M} (\SL_2\Z)$ of finite dimension.  
\begin{lemma}\label{lem:product_modular_forms}
	Let $f$ be a modular form of weight $k$ and $g$ a modular form of weight $l$, then 
	$fg$ is a modular form of weight  $k + g$.
\end{lemma}
\begin{proof}
	The three conditions from definition \ref{def:modular_form} must be verified. 
	\begin{enumerate}
		\item The product of holomorphic functions is holomorphic. So $ fg$ is holomorphic on $\mathcal{H} $. 
		\item Take any  $\gamma = \begin{pmatrix} a & b \\ c & d \end{pmatrix} \in \SL_2\Z$ and $\tau \in \mathcal{H} $. Then 
			\begin{align*}
				(fg)(\gamma \cdot \tau) &= f(\gamma \cdot \tau) g(\gamma \cdot \tau)   \\
							&= (c\tau + d)^{k} f(\tau) (c \tau)^{l} g(\tau) \\
							&= (c\tau + d)^{k+l} (fg)(\tau) \\
			.\end{align*}
			So $fg$ is weakly modular of weight $k+l$. 
		\item We know that $\lim_{\im(\tau) \to \infty} f(\tau)$, $\lim_{\im(\tau) \to \infty} g(\tau)$ exists and is finite. Hence $\lim_{\im(\tau) \to \infty} fg (\tau)$ exists and is finite.		
	\end{enumerate}
\end{proof}

Finally we introduce a special type of modular called a cusp. The names comes from connection to elliptic curves \todo{check that is are elliptic curves and not modular curves} that we will discuss later.
\begin{definition}\label{def:cusp}
	A \emph{cusp form} is a modular form $f$ (with respect to a congruence subgroup  $\Gamma$) such that for every  $\alpha \in \SL_2\Z$  the leading coefficient in its Fourier expansion is 0. 
	 The $\C$-vector space of cusp forms of weight $k$ is denoted $\mathcal{S} _k(\Gamma)$.
\end{definition}
Again, it is sufficient to check this for a representitive for every coset $\alpha \Gamma$.

\subsection{Examples of Modular Forms}
We may wonder whether these types of functions exist. One trivial modular form of weight $k$ is the zero function
, but the question remain whether there are non trivial modular forms of a given weight.
If $k$ is odd the answer is negative as $f(\tau) = f(-I_2 \tau) = (-1)^{k} f(\tau) = 0$. 
If we know a few modular forms of small weight, we can construct modular forms of higher weights using \cref{lem:product_modular_forms}.

However, we can construct a non trivial modular form for every even weight greater than 2.
\begin{definition}
	The \emph{Eisenstein series of weight $k$} ($k$ even and  $k >2$) is the function
	\begin{align*}
		G_k: \mathcal{H} &\longrightarrow \C \\
		\tau &\longmapsto \sum_{\substack{(c,d) \in \Z^2 \\ (c,d)\ne (0,0) }} \frac{1}{(c\tau + d)^{k}}
	.\end{align*}
\end{definition}
We of course have to check that this is indeed a modular form of weight $k$. 
Basic analysis can be used to show that the summation is absolutely convergent for every  $\tau \in \mathcal{H}$ and uniformly convergent on compact sets.
It follows that $G_k$ is holomorphic.
Recall from \cref{sec:defining_modular_forms} that it is suficient to check weak modularity for  $\gamma = \begin{pmatrix} 1 & 1 \\ 0 & 1 \end{pmatrix} $ and $\gamma = \begin{pmatrix} 0 & -1 \\ 1 & 0  \end{pmatrix} $, i.e.\ we have to show that \cref{eq:sufficient_weakly_modular} holds.
We see 
\begin{align*}
	G_k(\tau + 1) &= \sum_{\substack{(c, d) \in \Z^2 \\ (c, d) \ne (0,0)}} \frac{1}{(c (\tau + 1) + d)^{k}}\\
			 &= \sum_{\substack{(c, d) \in \Z^2 \\ (c, d) \ne (0,0)}} \frac{1}{(c \tau + (d+c))^{k}}\ \\
.\end{align*}
But this is just a permutation of the terms of the previous sequence, as $\Z^2 \to \Z^2: (c,d) \mapsto (c, c+ d)$ is a isomorphism of groups.
Hence $G_k(\tau + 1) = G_k(\tau)$.
We have to check the second equation as well.
\begin{align*}
	G_k\left(\frac{-1}{\tau}\right) &=  \sum_{\substack{(c,d) \in \Z^2 \\ (c,d) \ne 0}} \frac{1}{(-c / \tau + d)^{k}}\\
			     &= \tau^{k} \sum_{\substack{(c, d) \in \Z^2 \\ (c,d)}} \frac{1}{(d \tau - c)^{k}} \\
			     &= \tau^{k}G_k(\tau) \\
\end{align*}
The last equality is again true as we can permute the terms as the summation is absolutely convergent.

@@

\section{Lattices and Complex Elliptic Curves}
The main idea of this section is to construct tori by considering $\C$ as an additive group modulo a certain kind of embedding of $\Z^2$. This embedding of $\Z^2$ is called a lattice.  
\begin{definition}
	A \emph{lattice in $\C$} is additive subgroup $\Lambda = \omega_1 \Z \oplus \omega_2 \Z$ where $\omega_1, \omega_2 \in \C$ are linearly independent over $\R$ and $\omega_1 / \omega 2  \in \mathbb{H}$
\end{definition}
\begin{definition}
	A \emph{complex torus} is a quotient of the complex plane by a lattice, \[
		\C / \Lambda = \bigset{z + \Lambda}{z \in \C} 
	.\] 
\end{definition}
This object is called as torus because of a geometric intuition. 
If one considers the parallelogram spanned by $\vec{\omega_1}, \vec{\omega_2}$ we see that the opposing edges are `glued' together. 
So topologically this space is homeomorphic to the torus (see \cref{fig:complex_torus}).

@@

	By inverting the matrix we using completely analogous reasing that $\omega_1 \in \Lambda'$ and $\omega_2 \in \Lambda'$. So $\Lambda \subset \Lambda'$.
\end{proof}

@@

In our study of complex tori, holomorphic maps between them are of great importance. 
In light of this we want to know how such a maps look like. It turns our there linear transformations with some restrictions. 
\begin{proposition}
	Let $\phi: \C \ \Lambda \to \C \ \Lambda'$ be a holomorphic map between complex tori. 
	Then $\phi(z + \Lambda) = mz + b + \Lambda'$ for some $m, b \in \C$ such that $m \Lambda \subset  \Lambda'$. 
	The map is invertible if and only if $m \Lambda = \Lambda'$.
\end{proposition}
\begin{proof}
	The idea is to use topology to lift the map. As $\R^2 \simeq \C$ is the universal covering space of the torus we know that we can lift $\phi$ to a holomorphic map $\tilde \phi: \C / \Lambda \to \C$. We then can make this into a homolomorphism by first projecting $\C$ onto $\C / \Lambda$. We get a holomorphic map  $\tilde \phi: \C \to \C$.
	Take any $\lambda \in \Lambda$. 
	Then the map $f_\lambda(z) = \tilde\phi(z + \lambda) - \tilde \phi(z)$. We know that $f_{\lambda}$ is continous, but we also know that is must map to an element of $\Lambda'$, which is discrete, so it must be constant. 
	We can differentiate to find that $\tilde\phi'(z+ \lambda) = \tilde\phi'(z)$ for every $\lambda \in \Lambda$, hence it is  $\Lambda$ periodic.

	This makes $\tilde\phi'$ bounded so its constant. 
	So $\tilde \phi(z) = mz + b$ for some $m, b \in \C$. 
	Recall that $f_{\lambda}$ is is constant and equal to element of $\Lambda'$. 
	$\phi(z+\lambda) - \phi(z) = m\lambda \in \Lambda'$. 
	Hence $m \Lambda \subset \Lambda'$.

@@

\subsection{Modular Forms and Complex Tori} \label{sec:modular_forms_and_complex_tori}
We now have a notion of \emph{morphisms} between complex tori. We can now ask ourselves the question how equivalence classes of isomorphic complex tori look like.
It turns out that every complex torus $\C / \Lambda$ is \emph{isormorphic} to a torus of the form $\C / \Lambda_\tau$, where $\Lambda_\tau = \tau \Z \oplus \Z$, for some $\tau \in  \mathcal{H}$. 
Indeed, by definition $\Lambda = \omega_1 \Z \oplus \omega_2 \Z$ for some $\omega_1, \omega_2 \in \C$ such that $\omega_1 / \omega_2 \in \mathcal{H} $. Let $\tau = \omega_1 / \omega_2$. 
Then $\frac{1}{\omega_1} \Lambda = \Lambda_\tau$. 
So the map  \[
\phi: \frac{\C}{ \Lambda} \to \frac{\C}{\Lambda_\tau}: z + \Lambda \mapsto \frac{z}{\omega_1} + \Lambda_\tau
\]
is an isomorphism.

>>>>

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
%\usepackage[dutch]{babel}
\usepackage{amsmath, amssymb, amsthm}
%\usepackage{geometry}
\usepackage{tikz-cd}
\usepackage{mdframed}
\usepackage{color}
\usepackage{microtype}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{todonotes}
\usepackage[backend=biber]{biblatex}
\addbibresource{references.bib}
% figure support
\usepackage{import}
\usepackage{xifthen}
\usepackage{pdfpages}
\usepackage{transparent}
\newcommand{\incfig}[1]{%
	\def\svgwidth{\columnwidth}
	\import{./figures/}{#1.pdf_tex}
}

@@

\maketitle
\pagebreak

@@

This is the report of the journey of a student learning about elliptic curves. 
This report should be thought of as my notes while working my way through the first chapters of \emph{A First Course in Modular Forms} by Fred Diamond and Jerry Shurman\cite{diamondFirstCourseModular2005a}. 
This book is my main reference. 
Most of this report is paraphrasing this book, but I've added some details where I thought the book was lacking. 
I've also added some visual intuitions I developed to aid my understanding of this material. I hope potential readers will find these useful as well.

Unfortunately I did not get far enough into the subject to start studying more advanced subjects, due to the large amount of concepts, and relations between these concepts, that need to be understood first (the modular group, congruence subgroups, modular forms, complex tori, elliptic curves, modular curves, moduli spaces, \ldots). 
However this report should cover most if not all the prerequisites for understanding the more advanced topics.

@@

\begin{definition}
	The \emph{Modular group} are the $2\times 2$ matrices with integer coefficients and determinant $1$.
	 \[
		 \SL_2(\Z) =   \bigset{\begin{pmatrix} a& b\\ c& d \end{pmatrix}}{a, b, c, d \in \Z, ac - bd = 1}
	.\] 
\end{definition}
It can be shown that this is indeed a group and that it is generated by \[
	\begin{pmatrix}  1 & 1 \\ 0 & 1 \end{pmatrix} 
	\text{ and }
	\begin{pmatrix} 0 & -1 \\ 1 & 0 \end{pmatrix} 
.\] 
For a proof of this we refer to the appendices. 
We now define how this group acts on the complex half plane. 
\begin{definition}
	Let  $\gamma = \begin{pmatrix} a & b \\ c & d \end{pmatrix} $ be any element of $\SL_2\Z$ and $\tau$ be any element of $\mathcal{H} \cup \{\infty\} $.
	The multiplication of these two elements is defined as 
	\[
		\gamma(\tau) = \gamma \cdot \tau = \frac{a \tau + b}{ c \tau + d}
	.\] 
\end{definition}
Note that this group action is well defined. First we have to check that this every $\tau \in \mathcal{H} \cup \{\infty\}  $ gets mapped to another element of $\tau \in \mathcal{H} \cup \{ \infty\}$. 
Note that is is sufficient to check this for the action of the generators, which induce the maps \[
\tau \mapsto  \tau+1 \text{ and } \tau \mapsto \frac{-1}{\tau}
\]
for which it is obvious.
Further, we easily see that $I_2 \cdot \tau = \tau$. 
It also holds that for $\gamma = \begin{pmatrix} a & b \\ c & d \end{pmatrix} $ and $\beta = \begin{pmatrix} f & g \\ h & i \end{pmatrix} $: 
\begin{align*}
	\gamma \left( \beta \cdot  \tau\right) &=  \gamma\cdot \frac{f\tau + g}{h \tau + i} \\
					       &= \frac{a\left( \frac{f \tau + g}{h\tau + i} \right) + b}{c \left( \frac{f \tau + g}{h \tau + i} \right) + d} \\	
					       &= \frac{(af + bh)\tau + ga + bi}{(cf + dh) \tau + cg + di} \\
					       &= \begin{pmatrix} af + bh & ag + bi \\ cf + dh & cg + di \end{pmatrix} \cdot \tau \\
					       &= (\gamma \beta)\cdot \tau 
.\end{align*}

\subsection{Subgroups of the Modular Group} \label{sec:subgroups_of_the_modular_group}
Quite often it will be useful to restrict our focus to subgroups of the modular group. 
The type of subgroups of greatest interest are the so-called \emph{congruence subgroups}.
To define these we first have to define the so called \emph{principal congruence subgroups}.  
\begin{definition}
	For any $N \in \N$ we define the \emph{principal congruence subgroup of level $N$} to be \[
		\Gamma(N) = \bigset{\begin{pmatrix} a & b \\ c & d \end{pmatrix} \in \SL_2(\Z)}{\begin{pmatrix} a & b \\ c & d \end{pmatrix}  \equiv \begin{pmatrix} 1 & 0 \\ 0 & 1 \end{pmatrix}  (\mathrm{mod}\; N)}
	.\] 
\end{definition}

@@

Some meromorphic functions $f:\mathcal{H}  \to \hat{\C}$ are in some sense invariant under the action of the modular group (or one of its subgroups). 
These functions are the \emph{modular forms}.

@@

It's clearly enough so check \eqref{eq:weakly_modular} only for the generators of $\SL_2\Z$. I.e. check that
\begin{equation}\label{eq:sufficient_weakly_modular}
	f(\tau + 1) = f(\tau) \text{ and } f\left(-\frac{1}{\tau}\right)  = \tau^{k}f(\tau)
.\end{equation} 
From this we see that weakly modular functions are $\Z$ periodic.

We will now introduce the weight-$k$ operator on functions $[\gamma]_k$.
 \begin{definition}
	 Let $f: \mathcal{H}  \to \C$ be a function,  $\gamma = \begin{pmatrix} a & b \\ c & d \end{pmatrix} \in \SL_2\Z$ and $k \in \Z$ then we define the function $f[\gamma]_k$ to be 
	  \begin{align*}
		  f[\gamma]_k: \mathcal{H}  &\longrightarrow \C \\
		  \tau &\longmapsto (c\tau + d)^{-k}f(\gamma(\tau))
	 .\end{align*}
\end{definition}
This allows us to characterize  \emph{weakly modular of weight  $k$} as follows.
 \begin{lemma}
	 A function $f: \mathcal{H}  \to \C$ is weakly modular of weight $k$ if and only if for every $\gamma \in \SL_2$: \[
		 f[\gamma]_k = f
	 .\] 
\end{lemma}
In light of this characterization we extend to definition of weakly modular to congruence subgroups of $\SL_2\Z$.

\begin{definition}
	Let $\Gamma$ be a congruence subgroup of $\SL_2\Z$. We say that a function $f: \mathcal{H}  \to \C$ is \emph{weakly modular of weight $k$ with respect to $\Gamma$} if for every  $ \gamma \in \Gamma$:
	 \[
		 f[\gamma]_k = f 
	.\] 
\end{definition}

We are now ready to give the definition of a modular form. 
\begin{definition}\label{def:modular_form}
	Let $\Gamma$ be congruence subgroup of $\SL_2\Z$.
	A function $f: \mathcal{H}  \to \C$ is a \emph{modular form of weight $ k$ with respect to $\Gamma$} if 
	\begin{enumerate}
		\item $f$ is holomorphic on $\mathcal{H} $,
		\item $f$ is weakly modular of weight $k$ with respect to $\Gamma$, 
		\item $f[\gamma]_k$ is holomorphic at $\infty$ for every $\gamma \in \SL_2\Z$. 
	\end{enumerate}
	We denote the set of modular froms of weight $k$ with respect to $\Gamma$ as $\mathcal{M} _k(\SL_2\Z)$.

	If $\Gamma = \SL_2\Z$ we say simply that $f$ is a modular form of weight $k$. 
\end{definition}
The stament `holomorhic at $\infty$' deserves some explanation. 
One can show that any congruence subgroup contains a matrix of the form $\begin{pmatrix} 1 & k \\ 0 & 1 \end{pmatrix} $ ($\Gamma(N)$ contains  $\begin{pmatrix} 1 & n \\ 0 & 1 \end{pmatrix} $). 
If we choose this $k$ to be minimal we see that $f(\tau) = f(\tau + k)$. 
So $f$ is $k\Z$-periodic. It would be desirable if $f$ allowed a Fourrier expansion.  
There are many equivalent ways of defining `holomorphic at $\infty$', but for our purposes we will take this to mean that $f$ allows a Fourier expansion \footnote{The real picture behing holomopich at $\infty$ is that, due to $f$ being $k\Z$-periodic, $H$ can be 'rolled up' on the unit disk, where $\infty$ gets mapped to the center. In this picture  $f$ being holomorphic at $\infty$ means that  $f$ allows an extension which holomorphic on the center of the disk.}, i.e.\ \[
	f(\tau) = \sum_{n=0}^{\infty} a_n e^{n 2\pi i \tau / k}
,\]
for some $a_n \in \C$.
Another equivalent statement is that $\lim_{\im(\tau) \to \infty} f(\tau)$ exists and is finite.

Note that it is only necessary to verify the 3rd point of \cref{def:modular_form} for a representative of every coset $\alpha \Gamma$ as by the weak modularity  $f[\alpha]_k = f[\alpha \gamma]_k$ for every  $\gamma \in \Gamma$. 
If  $f$ is a modular form (so $\Gamma = \SL_2\Z$) then we just have to verify that $f$ is holomorphic at $\infty$.
Note that $\mathcal{M}(\Gamma)$ is a $\C$-vector space. 
It is the case that the last condition of \cref{def:modular_form} is what makes $\mathcal{M} (\SL_2\Z)$ of finite dimension, but I will not show this. 
\begin{lemma}\label{lem:product_modular_forms}
	Let $f$ be a modular form of weight $k$ and $g$ a modular form of weight $l$, then 
	$fg$ is a modular form of weight  $k + g$.
\end{lemma}
\begin{proof}
	The three conditions from definition \ref{def:modular_form} must be verified. 
	\begin{enumerate}
		\item The product of holomorphic functions is holomorphic. So $ fg$ is holomorphic on $\mathcal{H} $. 
		\item Take any  $\gamma = \begin{pmatrix} a & b \\ c & d \end{pmatrix} \in \SL_2\Z$ and $\tau \in \mathcal{H} $. Then 
			\begin{align*}
				(fg)(\gamma \cdot \tau) &= f(\gamma \cdot \tau) g(\gamma \cdot \tau)   \\
							&= (c\tau + d)^{k} f(\tau) (c \tau)^{l} g(\tau) \\
							&= (c\tau + d)^{k+l} (fg)(\tau) \\
			.\end{align*}
			So $fg$ is weakly modular of weight $k+l$. 
		\item We know that $\lim_{\im(\tau) \to \infty} f(\tau)$, $\lim_{\im(\tau) \to \infty} g(\tau)$ exists and is finite. Hence $\lim_{\im(\tau) \to \infty} fg (\tau)$ exists and is finite.		
	\end{enumerate}
\end{proof}

Finally we introduce a special type of modular called a cusp. The names comes from connection to modular curves that we will discuss later.
\begin{definition}\label{def:cusp}
	A \emph{cusp form} is a modular form $f$ (with respect to a congruence subgroup  $\Gamma$) such that for every  $\alpha \in \SL_2\Z$  the leading coefficient in its Fourier expansion is 0. 
	 The $\C$-vector space of cusp forms of weight $k$ is denoted $\mathcal{S} _k(\Gamma)$.
\end{definition}
Again, it is sufficient to check this for a representative for every coset $\alpha \Gamma$.

\subsection{Examples of Modular Forms}
We may wonder whether these types of functions exist. One trivial modular form of weight $k$ is the zero function, but the question remain whether there are non trivial modular forms of a given weight.
If $k$ is odd the answer is negative as $f(\tau) = f(-I_2 \tau) = (-1)^{k} f(\tau) = 0$. 
If we know a few modular forms of small weight, we can construct modular forms of higher weights using \cref{lem:product_modular_forms}.

However, we can construct a non trivial modular form for every even weight greater than 2.
\begin{definition}
	The \emph{Eisenstein series of weight $k$} ($k$ even and  $k >2$) is the function
	\begin{align*}
		G_k: \mathcal{H} &\longrightarrow \C \\
		\tau &\longmapsto \sum_{\substack{(c,d) \in \Z^2 \\ (c,d)\ne (0,0) }} \frac{1}{(c\tau + d)^{k}}
	.\end{align*}
\end{definition}
We of course have to check that this is indeed a modular form of weight $k$. 
Basic analysis can be used to show that the summation is absolutely convergent for every  $\tau \in \mathcal{H}$ and uniformly convergent on compact sets.
It follows that $G_k$ is holomorphic.
Recall from \cref{sec:defining_modular_forms} that it is sufficient to check weak modularity for  $\gamma = \begin{pmatrix} 1 & 1 \\ 0 & 1 \end{pmatrix} $ and $\gamma = \begin{pmatrix} 0 & -1 \\ 1 & 0  \end{pmatrix} $, i.e.\ we have to show that \cref{eq:sufficient_weakly_modular} holds.
We see 
\begin{align*}
	G_k(\tau + 1) &= \sum_{\substack{(c, d) \in \Z^2 \\ (c, d) \ne (0,0)}} \frac{1}{(c (\tau + 1) + d)^{k}}\\
			 &= \sum_{\substack{(c, d) \in \Z^2 \\ (c, d) \ne (0,0)}} \frac{1}{(c \tau + (d+c))^{k}}\ \\
.\end{align*}
But this is just a permutation of the terms of the previous sequence, as $\Z^2 \to \Z^2: (c,d) \mapsto (c, c+ d)$ is a isomorphism of groups.
Hence $G_k(\tau + 1) = G_k(\tau)$.
We have to check the second equation as well.
\begin{align*}
	G_k\left(\frac{-1}{\tau}\right) &=  \sum_{\substack{(c,d) \in \Z^2 \\ (c,d) \ne 0}} \frac{1}{(-c / \tau + d)^{k}}\\
			     &= \tau^{k} \sum_{\substack{(c, d) \in \Z^2 \\ (c,d)}} \frac{1}{(d \tau - c)^{k}} \\
			     &= \tau^{k}G_k(\tau) \\
\end{align*}
The last equality is again true as we can permute the terms as the summation is absolutely convergent.

@@

\section{Lattices and Complex Elliptic Curves}
The main idea of this section is to construct tori by considering $\C$ as an additive group modulo a certain kind of embedding of $\Z^2$. This embedding of $\Z^2$ is called a lattice.  
\begin{definition}
	A \emph{lattice in $\C$} is additive subgroup $\Lambda = \omega_1 \Z \oplus \omega_2 \Z$ where $\omega_1, \omega_2 \in \C$ are linearly independent over $\R$ and $\omega_1 / \omega_2  \in \mathcal{H}$.
\end{definition}
\begin{definition}
	A \emph{complex torus} is a quotient of the complex plane by a lattice, \[
		\C / \Lambda = \bigset{z + \Lambda}{z \in \C} 
	.\] 
\end{definition}
This object is called as torus because of a geometric intuition. 
If one considers the parallelogram spanned by $\vec{\omega_1}, \vec{\omega_2}$ we see that the opposing edges are `glued' together. 
So topologically this space is homeomorphic to the torus (see \cref{fig:complex_torus}).

@@

	By inverting the matrix a completely analogous argument shows that $\omega_1 \in \Lambda'$ and $\omega_2 \in \Lambda'$. So $\Lambda \subset \Lambda'$.
\end{proof}

@@

In our study of complex tori, holomorphic maps between them are of great importance. 
In light of this we want to know how such a maps look like. It turns out they are linear transformations with some restrictions. 
\begin{proposition}
	Let $\phi: \C \ \Lambda \to \C \ \Lambda'$ be a holomorphic map between complex tori. 
	Then $\phi(z + \Lambda) = mz + b + \Lambda'$ for some $m, b \in \C$ such that $m \Lambda \subset  \Lambda'$. 
	The map is invertible if and only if $m \Lambda = \Lambda'$.
\end{proposition}
\begin{proof}
	The idea is to use topology to lift the map. As $\R^2 \simeq \C$ is the universal covering space of the torus we know that we can lift $\phi$ to a holomorphic map $\tilde \phi: \C / \Lambda \to \C$. We then can make this into a homolomorphism by first projecting $\C$ onto $\C / \Lambda$. We get a holomorphic map  $\tilde \phi: \C \to \C$.
	Take any $\lambda \in \Lambda$. 
	Then the map $f_\lambda(z) = \tilde\phi(z + \lambda) - \tilde \phi(z)$. We know that $f_{\lambda}$ is continous, but we also know that is must map to an element of $\Lambda'$, which is discrete, so it must be constant. 
	We can differentiate to find that $\tilde\phi'(z+ \lambda) = \tilde\phi'(z)$ for every $\lambda \in \Lambda$, hence it is  $\Lambda$ periodic.

	This makes $\tilde\phi'$ bounded so its constant. 
	So $\tilde \phi(z) = mz + b$ for some $m, b \in \C$. 
	Recall that $f_{\lambda}$ is is constant and equal to an element of $\Lambda'$. 
	$\phi(z+\lambda) - \phi(z) = m\lambda \in \Lambda'$. 
	Hence $m \Lambda \subset \Lambda'$.

@@

\subsection{Modular Forms and Complex Tori} \label{sec:modular_forms_and_complex_tori}
We now have a notion of \emph{morphisms} between complex tori. We can now ask ourselves the question how equivalence classes of isomorphic complex tori look like.
It turns out that every complex torus $\C / \Lambda$ is \emph{isomorphic} to a torus of the form $\C / \Lambda_\tau$, where $\Lambda_\tau = \tau \Z \oplus \Z$, for some $\tau \in  \mathcal{H}$. 
Indeed, by definition $\Lambda = \omega_1 \Z \oplus \omega_2 \Z$ for some $\omega_1, \omega_2 \in \C$ such that $\omega_1 / \omega_2 \in \mathcal{H} $. Let $\tau = \omega_1 / \omega_2$. 
Then $\frac{1}{\omega_1} \Lambda = \Lambda_\tau$. 
So the map  \[
\phi: \frac{\C}{ \Lambda} \to \frac{\C}{\Lambda_\tau}: z + \Lambda \mapsto \frac{z}{\omega_1} + \Lambda_\tau
\]
is an isomorphism.
